Ms. No. PSRM-OA-2019-0126 entitled ``Taking Dyads Seriously''

### 2020-03-02 revisionMemo/rev1.tex
memo edits again
slight memo changes

		\item  \emph{

@@

		\item {\emph{

@@

@@

		\item  \emph{
For part (a), we have clarified that our study does not address causal identification. We instead focus on providing unbiased estimates of covariates, which improves inference for observational data. We have also edited P8 to read: Non-iid observations in relational data result from the fact that there is a complex structure underlying the dyadic events or processes that we observe. We have also clarified the goals of the paper in the earlier sections.}
		\item \emph{\textcolor{blue}{As for (b), the reviewer raises an important point. How well does AME work out when the DGP does not abide by parametric assumptions...relates to SM's to-do below.}}
		\item \emph{\textcolor{blue}{Finally, we understand these goals are not always central to political science research, but we believe that prediction is both a valuable metric to evaluate model performance as well as a goal for scholars in and of itself, as in Gleditsch and Ward 2013; Grimmer 2015; Neunhoeffer and Sternberg 2019; Colaresi and Mahmood 2017; Mueller and Rauh 2018. CD: Do I add this to text somewhere or leave as memo only?}

>>>>

		\item  \emph{ \textcolor{blue}{

@@

		\item {\emph{\textcolor{blue}{

@@

		}}}

@@

		\item  \emph{\textcolor{blue}{
For part (a), we have clarified that our study does not address causal identification. We instead focus on providing unbiased estimates of covariates, which improves inference for observational data. We have also edited P8 to read: Non-iid observations in relational data result from the fact that there is a complex structure underlying the dyadic events or processes that we observe. We have also clarified the goals of the paper in the earlier sections.}}
		\item \emph{\textcolor{blue}{As for (b), the reviewer raises an important point. How well does AME work out when the DGP does not abide by parametric assumptions we address this in the section concerning the simulation and Aronow's approach.}}
		\item \emph{\textcolor{blue}{Finally, we understand these goals are not always central to political science research, but we believe that prediction is both a valuable metric to evaluate model performance as well as a goal for scholars in and of itself, as in Gleditsch and Ward 2013; Grimmer 2015; Neunhoeffer and Sternberg 2019; Colaresi and Mahmood 2017; Mueller and Rauh 2018.}
